\documentclass[12pt]{article}
% -----------------------------------------------------------------------
\def \address{2287 S. Main St.\\Ann Arbor, MI}
\def \author{Nigel Baillie}
\def \email{bnigel@umich.edu}
\def \phonenumber{(734) 678-5328}
\def \bday{Born April $11^{\text{th}}$ 1995}
\def \github{github.com/Resonious}
% -----------------------------------------------------------------------
\reversemarginpar

\usepackage[paper=letterpaper,  marginparwidth=5mm,
            marginparsep=1.5mm, margin=1in,
            noheadfoot,         top=10mm,
            pdftex]{geometry}
            
\usepackage{mathtools}            
\usepackage{blindtext}

% No indenting paragraphs
\setlength{\parindent}{0in}

\usepackage{fancyhdr}
\pagestyle{fancy}
\pagestyle{empty}
\usepackage{color,hyperref}

% ------------------------- Helpers ------------------------------------ %
\renewcommand{\section}[1]{{\Huge{#1}}\vspace{2 mm}}

\newenvironment{nontimeline}
        {\begin{tabular}{|p{171 mm}}}
        {\end{tabular}}

\newenvironment{timeline}
        {\begin{tabular}{p{21 mm}|p{150 mm}}}
        {\end{tabular}}

\newenvironment{timelinetitle}
        {\vspace{-2 mm}\begin{large}}
        {\end{large}\vspace{-1.5 mm}}

\newcommand{\timespan}[2]{{#2}\newline{#1}}

\newcommand{\hlinewidth}{0.01pt}

\newcommand{\resumeitem}{\newline\vspace{3 mm}\hspace{3 mm}}

% ------------------------- Document ----------------------------------- %
\begin{document}
\newlength{\rcollength}\setlength{\rcollength}{3.0in}%
\begin{tabular} {
  p{\textwidth/3-\marginparwidth+2mm}
  p{\textwidth/3-\marginparwidth+2mm}
  p{\textwidth/3-\marginparwidth+2mm}
}
  \begin{flushleft}
    {\Huge{\author}}\\
    \vspace{1.5 mm}
  \end{flushleft}
  &
  \begin{center}
    {\phonenumber}\\
    {\email}\\
    {\github}
  \end{center}
  &
  \begin{flushright}
    {\bday}\\
    {\address}
  \end{flushright}
\end{tabular}
% --------------------------- Cover Letter -----------------------------------

Mr. Zak McClendon
\newline
Lead Game Designer
\newline
Double Fine Productions, Inc.
\newline

Dear Zak McClendon:
\newline

I write to express interest in joining Double Fine as a gameplay programmer,
as per the listing on your website.
I'm currently a web developer at a local small business, and also a college
student studying Computer Science at the University of Michigan. In addition
to my professional and academic profile, I have been practicing game programming
for fun since I was sixteen and have been playing games for as long as I can
remember. Between my job, schooling, and hobby, I have developed a diverse
set of general programming and game development skills.
\newline

% Hobby paragraph
To bring to the Double Fine table, I have solid hobbyist experience Unity,
Unreal Engine 4, and SDL2, in addition to some 2D JavaScript libraries.
Most notably Unreal Engine 4, of course, as I believe that is the backbone of
Psychonauts 2. The project I used UE4 in was a Ludum Dare game jam
entry, a side scrolling puzzle platformer in which the player arranges
mirrors to redirect beams of light with special abilities. For instance,
the purple rays propel the player in the direction they point. The game
was developed mostly using Unreal's C++ interface and later I integrated
the C++ functionality with Blueprint for quick prototyping. I found the Blueprint
system is surprisingly fun to work with.
\newline

% Segway into job
I'm no mathematician but I am plenty capable at mathematically involved
tasks. I tought myself OpenGL and the Rust programming language by creating
a 2D batching sprite renderer that supports scale, rotation about a point, and
hue adjustment on the shader level. In addition to my hobby projects, my profession
although not specifically games related, has provided me 3 years of solid
software engineering experience in areas such as databases, deployment, user
interface, and error reporting. I even wrote an image compositor for custom t-shirt
mockups that outperforms ImageMagick by about $1.5\times$.
\newline

% FINALE ?
While a games company probably doesn't often write their own CPU compositor,
I \\ think the under-the-hood knowledge does bear some meaning. More specifically,
a step towards a more thorough understanding of the systems we work with.
On the off chance that you'd like a more thorough understanding of the systems
\textit{I've} worked with, see the enclosed resume. I like what you guys do at
Double Fine, and I'd be honored to join you. If you don't mind, I'll give you guys
a call in a couple weeks when you've had time to think things through.
\newline

Sincerely,
\newline
Nigel


\pagebreak

% ---------------------------- Resume ----------------------------------------

% TODO put name on the resume

\begin{tabular} {
  p{\textwidth/3-\marginparwidth+2mm}
  p{\textwidth/3-\marginparwidth+2mm}
  p{\textwidth/3-\marginparwidth+2mm}
}
  \begin{flushleft}
  \end{flushleft}
  &
  \begin{center}
    {\Huge{\author}}\\
  \end{center}
  &
  \begin{flushright}
  \end{flushright}
\end{tabular}

\section{Objective:} Make a GOOD VIDEO GAMES
\newline

\section{Education}
\hline

\begin{timeline}
\timespan{Sept. 2016}{April 2018}
&
\begin{timelinetitle}
    University of Michigan
\end{timelinetitle}
\hspace{16mm}
B.S.E. Computer Science Engineering
\vspace{3 mm}

\\

\timespan{Sept. 2012}{May 2016}
&
\begin{timelinetitle}
    Washtenaw Community College
\end{timelinetitle}
\hspace{29mm}
Transferred to U-M

\end{timeline}
% ----------------------------------------------------------------------------

\vspace{3.0 mm}
\section{Employment}
\hline
% ----------------------------------------------------------------------------

\begin{timeline}
\timespan{Feb. 2014}{Present}
&
\begin{timelinetitle}
    Intermediate Developer at Ann Arbor T-Shirt Company
\end{timelinetitle}
\vspace{1 mm}

\resumeitem I develop features and bug fixes for our quote building software,
      production tracker, online store, and main website using \textbf{Ruby on Rails}.

\resumeitem Wrote mobile app for quick pricing using \textbf{React Native}.

\resumeitem \textbf{Proposed} and implemented unified authentication system to provide a single
      sign-in for all in-house apps.

\resumeitem Built domain specific image composition tool that out-performs ImageMagick
      at generating t-shirt mockups by about $1.5\times$ using \textbf{C++} and libpng.

\resumeitem Set up \textbf{continuous integration} for automatic testing and deployment of
      our Rails apps.

\end{timeline}
% ----------------------------------------------------------------------------

\vspace{3.0 mm}
\section{Hobby}
\hline
% ----------------------------------------------------------------------------

\begin{timeline}
\timespan{2011}{Present}
&
\begin{timelinetitle}
    Miscellaneous Game Development
\end{timelinetitle}
\begin{itemize}
  \item Participated in 3 \textbf{Ludum Dare} competitions (solo) and 1 jam (team.)

  \item Built a pixel-perfect platformer \textbf{collision detection} system based on
        the old Sonic the Hedgehog games for Sega Genesis.

  \item Implemented a lockstep-like \textbf{networking} protocol for said platformer
        using raw UDP (and TCP) sockets.

  \item Built a small 2D sprite renderer in the \textbf{Rust} programming language using
        \textbf{OpenGL} (``gl'' crate.)

  \item Wrote a runtime \textbf{JVM bytecode} injection routine for a Minecraft mod to disable
        collision.
\end{itemize}

\end{timeline}

\end{document}
