\documentclass[11pt]{article}
\renewcommand{\familydefault}{\sfdefault}
% -----------------------------------------------------------------------
\def \address{2287 S. Main St. Ann Arbor, MI}
\def \author{Nigel Baillie}
\def \email{bnigel@umich.edu}
\def \phonenumber{(734) 678-5328}
\def \github{https://github.com/Resonious}
\def \homepage{https://nigelbaillie.me}
% -----------------------------------------------------------------------
\reversemarginpar

\usepackage[paper=letterpaper,  marginparwidth=5mm,
            marginparsep=1.5mm, margin=15mm,
            noheadfoot,         top=5mm,
            pdftex]{geometry}

\usepackage{mathtools}            
\usepackage{blindtext}
\usepackage{url}

% No indenting
\setlength{\parindent}{0in}

\usepackage{fancyhdr}
\pagestyle{fancy}
\pagestyle{empty}
\usepackage{color,hyperref}

% ------------------------- Helpers ------------------------------------ %
\renewcommand{\section}[1]{{\LARGE{#1}}\vspace{2 mm}}

\newenvironment{nontimeline}
        {\begin{tabular}{|p{171 mm}}}
        {\end{tabular}}

\newenvironment{timeline}
        {\begin{tabular}{p{21 mm}|p{150 mm}}}
        {\end{tabular}}

\newenvironment{timelinetitle}
        {\vspace{-2 mm}\begin{large}}
        {\end{large}\vspace{-1.5 mm}}

\newcommand{\timespan}[2]{{#2}\newline{#1}}

\newcommand{\hlinewidth}{0.01pt}

% ------------------------- Document ----------------------------------- %
\begin{document}
\newlength{\rcollength}\setlength{\rcollength}{3.0in}%
\begin{tabular} {
  p{\textwidth/3-\marginparwidth+2mm}
  p{\textwidth/3-\marginparwidth+2mm}
  p{\textwidth/3-\marginparwidth+2mm}
}
  \begin{flushleft}
    {\address}\\
    {\phonenumber}
  \end{flushleft}
  &
  \begin{center}
    {\Huge{\author}}\\
    \vspace{1.5 mm}\\
    {\email}
  \end{center}
  &
  \begin{flushright}
    {\github}\\
    {\homepage}
  \end{flushright}
\end{tabular}
% ----------------------------------------------------------------------------

\section{Education}
%\hline

\begin{timeline}
\timespan{Sept 2016}{May 2019}
&
\begin{timelinetitle}
  University of Michigan --- \small{GPA: 3.2}
\end{timelinetitle}
\begin{itemize}
  \item[] \textbf{Degree:} Computer Science BSE.
  \item[] \textbf{Courses:} Computer architecture, operating systems, computer security, video game development, artificial intelligence.
\end{itemize}
\end{timeline}
% ----------------------------------------------------------------------------

\vspace{3.0 mm}
\section{Employment}
%\hline
% ----------------------------------------------------------------------------

\begin{timeline}
\timespan{Feb 2014}{Sept 2018}
&
\begin{timelinetitle}
  \textbf{Software Developer} \small{at Ann Arbor T-Shirt Company}
\end{timelinetitle}
\begin{itemize}
  \item[] Developed features and fixes in a small team for quote building software,
        production tracker, and retail backend using Ruby on Rails.

      \item[] Improved image composition tool in C++ using libpng. $1.5\times$ speedup over original.

      \item[] Set up and managed AWS Virtual Private Cloud infrastructure.

      \item[] Programmed Arduino to control fans based on temperature for screen drying.
  
      \item[] Integrated with several $3^\text{rd}$ party APIs for services including Shopify, Amazon, PayPal.

      \item[] Implemented robust error reporting and handling across apps.

\end{itemize}

\end{timeline}
% ----------------------------------------------------------------------------

\vspace{3.0 mm}
\section{Extracurricular}
%\hline
% ----------------------------------------------------------------------------

\begin{timeline}
\timespan{2011}{Always}
&
\begin{timelinetitle}
    Small 2D Sprite Renderer in Rust+OpenGL
\end{timelinetitle}
\begin{itemize}
  \item[] GLFW for window management and runtime code reloading:
    \begin{itemize}
      \item Main loop in executable, game code in dynamic library. Main loop waits for updated DLL, then re-loads symbols and recompiles shaders.
    \end{itemize}
\end{itemize}

\vspace{0.5cm}

\begin{timelinetitle}
    JVM Bytecode Patching for Minecraft Mod
\end{timelinetitle}
\begin{itemize}
  \item[] Used \texttt{org.objectweb.asm} namespace to traverse instructions for each class.
  \item[] Patched entity collision method to potentially return early after performing a test.
\end{itemize}

\vspace{0.5cm}

\begin{timelinetitle}
    Wine (winehq.org) Shell Notification Bugfix
\end{timelinetitle}
\begin{itemize}
  \item[] The bug: ``new folder'' button didn't always show the new folder.
  \item[] Traced back to unimplemented behavior in \texttt{SHChangeNotifyRegister}.
\end{itemize}

\end{timeline}

\vspace{3.0 mm}

\begin{tabular}{l l l}
  \section{Languages} & \section{Technologies} & \section{School Projects} \\

  C, C++, C\#, Java, Ruby, Python,
  &
  MacOS, Linux, Windows
  &
  Multiplayer game in team of 4.
  \\

  SQL, Rust, Prolog, Verilog,
  &
  Unity3D, Unreal Engine, Godot,
  &
  Thread library, memory pager, filsystem.
  \\

  HTML, CSS, Javascript, \LaTeX
  &
  Visual Studio, GNU Make, Git,
  &
  NES controller interface circuit.
  \\


  &
  Wireguard, OpenVPN
  &
  \\
\end{tabular}

\end{document}
